---
pagetitle: "Adrià Mitjavila Ventura"
title: "<b style='color:black;'>Publications</b>"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      error = FALSE,
                      warning = FALSE, 
                      fig.align = "center")
```

```{r echo=FALSE, eval=FALSE}
***
<p style='font-size:15px; color:black;'>Go to:</p>

* [Journal articles](#papers)

* [Posters](#posters)
```

***

# <b style='font-size:25px; color:black;'>Journal articles</b> {#papers} 

* <p style='font-size:15px;'> Begley V, Jordán-Pla A, Peñate X, Godino-Garrido A, Challal D, Cuevas-Bermúdez A, <ins style="color:Tomato;">Mitjavila A</ins>, Barucco Mara, Gutiérrez G, Singh A, Alepuz P, Navarro F, Libri D, Pérez-Ortín JE, Chávez S (2020). **Xrn1 influence on gene transcription results from the combination of general effects on elongating RNA pol II and gene-specific chromatin configuration**. [Preprint](https://www.biorxiv.org/content/10.1101/2020.06.02.129171v2) in *bioRxiv*. doi: https://doi.org/10.1101/2020.06.02.129171 </p>

# <b style='font-size:25px; color:black;'>Posters</b> {#posters}

<p style='font-size:15px;'> At the moment, I do not have any presented posters.</p>
