---
title: "<b>Adrià Mitjavila Ventura</b>"
output: 
  html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      error = FALSE,
                      warning = FALSE)
```


```{r image_me, eval=TRUE}
htmltools::img(src = "assets/lm2x_wrci.png", 
               style = 'float; position:absolute; top:1; right:0; padding-top: 20px; padding-right: 420px; height:200px')
```

***

<p style = "font-size:20px;">(ex-elite) Rower</p>

<p style = "font-size:20px;">Club Natació Banyoles & Spanish Rowing Team</p>

<p style = "font-size:20px;">2016 World Rowing Under-23 Champion in BLM2x</p>

***

## Rowing {.tabset}


### 2018/2019

* European Rowing Championship
    + LM4x - **7^th^** - ESP <br><br>

* Spanish Rowing Championship
    + M8+ - **2^nd^** - BNY <br><br>
    
* Catalan Rowing Championship
    + M8+ - **1^st^** - BNY 
    + M4- - **3^rd^** - BNY 
    + M4x - **1^st^** - BNY <br><br>
    
* Spring trial (entry to national team)
    + LM1x - **1^st^** - BNY <br><br>
    
* Spanish Rowing Championship by Autonomies
    + M8+ - **1^st^** - CAT <br><br>

### 2017/2018

* Mediterranean Games
    + LM2x - **2^nd^** - ESP <br><br>

* Spanish Rowing Championship
    + M4x - **1^st^** - BNY
    + M8+ - **4^th^** - BNY <br><br>
    
* Catalan Rowing Championship
    + M8+ - **1^st^** - BNY 
    + M4- - **2^nd^** - BNY 
    + M4x - **1^st^** - BNY 
    + M2x - **3^rd^** - BNY <br><br>

* Spring trial (entry to national team)
    + LM1x - **3^rd^** - BNY <br><br>
 
### 2016/2017



### 2015/2016

* World Rowing Under-23 Championship
    + BLM2x - **1^st^** - ESP <br><br>
    
* European Continental Olympic Qualification Regatta
    + LM2x - **4^th^** - ESP <br><br>

* World Rowing Cup I
    + LM2x - **5^th^** - ESP <br><br>

* *Regatta internazionale di Piediluco - XXX Memorial Paolo d’Aloja*
    + LM2x - **2^nd^** - ESP
    + LM2x - **2^nd^** - ESP <br><br>

* Spanish Rowing Championship
    + M4x - **2^nd^** - BNY 
    + M2x - **2^nd^** - BNY <br><br>
    
* French Rowing Championship
    + M4x - **2^nd^** - PER <br><br>
    
* Catalan Rowing Championship
    + M8+ - **2^nd^** - BNY 
    + M2x - **1^st^** - BNY 
    + M4x - **1^st^** - BNY <br><br>
    
* Spring trial (entry to national team)
    + M1x - **7^th^** - BNY <br><br>

* Spanish Long Distance Rowing Championship
    + LM1x - **4^th^** - BNY <br><br>

* Spanish Indor Rowing Championship
    + LM - **5^th^** - BNY <br><br>

### 2014/2015

* World Rowing Under-23 Championship
    + BLM2x - **6^th^** - ESP <br><br>

* *Regatta internazionale di Piediluco - XXX Memorial Paolo d’Aloja*
    + LM2x - **4^th^** - ESP <br><br>
    
* *Régate internationale Savoie – Mont-blanc*
    + M2x - **2^nd^** - CAT
    + M4x - **1^st^** - CAT <br><br>

* Spanish Rowing Championship
    + M2x - **2^nd^** - BNY <br><br>
    
* French Rowing Championship
    + M4x - **7^th^** - PER <br><br>
    
* Catalan Rowing Championship
    + M8+ - **1^st^** - BNY 
    + M2x - **1^st^** - BNY 
    + M4x - **1^st^** - BNY <br><br>
    
* Spring trial (entry to national team)
    + M1x - **6^th^** - BNY <br><br>

* Spanish Indor Rowing Championship
    + LM - **4^th^** - BNY <br><br>
    
* *Défi Seine*
    + M8+ - **3^rd^** - BNY <br><br>

### 2013/2014

* World Rowing Under-23 Championship
    + BLM2x - **13^th^** - ESP <br><br>

* *Régate internationale Savoie – Mont-blanc*
    + M2x - **1^st^** - CAT
    + M4x - **2^nd^** - CAT <br><br>

* Spanish Rowing Championship
    + M2x - **1^st^** - BNY
    + M8+ - **6^th^** - BNY <br><br>
    
* Catalan Rowing Championship
    + M8+ - **1^st^** - BNY 
    + M2x - **1^st^** - BNY 
    + M4x - **1^st^** - BNY <br><br>
    
* Spring trial (entry to national team)
    + M1x - **6^th^** - BNY <br><br>

* Spanish Indor Rowing Championship
    + LM - **7^th^** - BNY <br><br>

* Rowing Avignon Cup Edition
    + M8+ - **6^th^** - BNY
    + M2x - **2^nd^** - BNY <br><br>

### 2012/2013

### 2011/2012

### 2010/2011

### 2009/2010

### 2008/2009

### 2007/2008

### Abbreviations

```{r abbreviations, echo=FALSE}
library(dplyr)

data.frame(Category = c("M: Men", "LM: Lightweight men", "BM:  Under-23 men", "BLM: Under-23 lightweight men", 
                        "JM: Junior men", "CM: Under-17 men", "IM: Under-15 men", "AM: Under-13 men"),
           Boat = c("8+: Coxed eight", "4+:  Coxed four", "4-: Coxless four", "4x: Quadruple scull", 
                    "2+: Coxed pair", "2-:   Coxless pair", "2x   Double scull", "1x:  Single scull"),
           Team = c("ESP: Spanish Rowing Team", "CAT: Catalan Rowing Team", "BNY: Club Natació Banyoles", "PER: Aviron Perpignan 66", " ", " ", " ", " ")) %>%
  
  knitr::kable()

```
